Draft information

### 2019-05-06 paper/draft-info.Rmd
Update draft info

* Suggest a justification for the traits used if needed (see \lr{M-justification-traits}).
* Identify sections/sentences to trim to achieve the word limit.
* Suggest a reference for sentence in \lr{M-ref-interaction-strength} if needed.
* Suggest a reference for sentence in \lr{M-ref-plant-flexibility} if needed. 
* Suggest alternative, more-appropiate, sub-headings if needed. 
* Check statement in \lr{M-theoretical-models}

@@

* Added .git and .drake to .dockerignore to speed up build
* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
* Many minor changes to the text
* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology).

>>>>

* Specify grant numbers in the Awknoledgements and make sure the ones stated there now are correct. 
* Aprove (or not for submission)

@@

* Added .git and .drake to .dockerignore to speed up build
* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
* Many minor changes to the text
* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology). 
* Some extra refs added
* Moved the sentences about variable collinearity to the supp. info. to save a bit of space in the main text
* Removed criteria #2...
